The Next Generation of Canadian Salmon

### 2024-04-19 output/paper.qmd
cite testthat

For additional assistance with data storage, the `arrow` [@citearrow] was used and for report generation, the `knitr` [@citeknitr] package was used.

>>>>

For additional assistance with data storage, the `arrow` [@citearrow] package was used and for report generation, the `knitr` [@citeknitr] package was used. For testing / verifying data the `testthat` [@citetestthat] package was used.
